---
title: "quickReg"
author: "Xikun Han,  <Xikun.Han@qimrberghofer.edu.au>"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    css: quickReg.css
vignette: >
  %\VignetteIndexEntry{quickReg}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

A manual to show the R package `quickReg`.


##Introduction
The `quickReg` package concentrates on a set of functions to display and pry a dataset. More precisely, the package can display statistical description for a dataset, build univariate regression models for lm, glm and cox regression based on specified variables. More importantly, the package provides several seamless functions to display these regressions. Several examples are used to explain the idea.


##Getting started
The example data is a hypothetical dataset extracting a subset from package [PredictABEL](http://www.genabel.org/packages/PredictABEL). It has no practical implications and only be used to demostrate the main idea of the package.


```{r set, echo=FALSE}
# Change the width of html file
options(width = 150)

```


```{r data}

# If you haven't install the package, you can download it from cran

# install.packages("quickReg")

library(quickReg)

# Load the dataset

data(diabetes)

# Show the first 6 rows of the data

head(diabetes)

```

We can use  the function **diaplay** to show statistical descriptions of the data.

```{r display}

show_data<-display(diabetes)

# We can show the results with indices or just the name of variables

show_data[1:2]

show_data$BMI

```



## Build regression models


```{r quickReg}

# Apply univariate regression models

reg_glm<-reg(data = diabetes, y = 5, factor = c(1, 3, 4), model = 'glm')

# reg_glm have two componets, the regression models in detail and a concentrated data frame

# We can show the detail information with: reg_glm$detail, detail(reg_glm)

reg_glm$detail$BMI

# To show the concentrated data frame: reg_glm$dataframe, dataframe(reg_glm)

dataframe(reg_glm)

# Linear model and cox regression model are also avaiable

reg_lm<-reg(data = diabetes, x = c(1:6,8:12), y = 7, factor = c(1, 3, 4), model = 'lm')

# Use varible names
reg_coxph<-reg(data = diabetes, y = "diabetes", time = "age", factor = c("sex", "smoking", "education"), model = 'coxph')


# Display could be used to a reg class to summarize univariate models

display(reg_glm)

display(reg_lm)

display(reg_coxph)

```




## Plot regression models


```{r plot,fig.width=8,fig.height=5}

# `quickReg` package provides forest plot for univariate regression models

plot(reg_glm)

# One OR value is larger than others, we can set the limits
plot(reg_glm,limits=c(NA,3))

plot(reg_glm,limits=c(1,2))

# Sort the variables according to alphabetical

plot(reg_glm,limits=c(NA,3), sort ="alphabetical")

# Similarly, we can plot lm and cox regression results

plot(reg_lm,limits=c(-2,5))

plot(reg_coxph,limits=c(0.5,2))

# Modify plot.reg like ggplot2, add themes from package `ggthemes` 
library(ggplot2);library(ggthemes)

plot(reg_coxph,limits=c(0.5,2))+
  labs(list(title = "Logistic Regression Model", x = "variables"))+
  theme_classic() %+replace% 
  theme(legend.position ="none",axis.text.x=element_text(angle=45,size=rel(1.5)))

```



## Perspective

The `quickReg` package provides a flexible and convenient way to dispaly data and the association between variables. This vignette offers a glimpse of its use and features. The source code and help files are more helpful. The package is ongoing. Seamless subgroup analysis, more regression types and  adjusted models may be avaliable in the future. Please contact me with any comments, questions and bug reports.


